Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-03-15 Scripts/evaluating_pca.Rmd
added loop to save plots

```{r}

>>>>

```{r}
fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/10kb/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""))

#file names for heatmaps
heatnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""))

#file names for pca plots
scorepnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""))

for(i in 1:length(fileslst)){
  pcadata <- readRDS(fileslst[i])

  #performing log2 transformation only for distance predictor types
  if(grepl("_dist", colnames(pcadata)[1])){
    pcadata <- apply(pcadata,2,function(x){log(x + 1, base=2)})
  }

  #filtering low variance predictors
  nzv <- nearZeroVar(pcadata, saveMetrics= TRUE)
  nzvar <- rownames(nzv[nzv$nzv,])
  if(length(nzvar) > 0){ 
    pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
    }

  #cleaning column names
  colnames(pcadata_f) <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878",
                                                    "K562", 
                                                    "dist",
                                                    "count",
                                                    "perc",
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", colnames(pcadata_f))

  #heatmap 
  #my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
  #png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", heatnames[i], sep=""),
  #    width=11, height=8, units="in")
  #heatmap.2(pcadata_f,
  #        #cellnote = ,  # same data set for cell labels
  #        #main = "", # heat map title
  #        notecol="black",      # change font color of cell labels to black
  #        density.info="none",  # turns off density plot inside color legend
  #        trace="none",         # turns off trace lines inside the heat map
  #        #margins =c(5,5),     # widens margins around plot
  #        col=my_palette,       # use on color palette defined earlier
  #        #na.color = "gray",
  #        #breaks=col_breaks,    # enable color transition at specified limits
  #        key=TRUE,
  #        dendrogram="column",     # only draw a row dendrogram
  #        cexRow=0.5,
  #        cexCol=0.5,
  #        labRow = FALSE,
  #        #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
  #        #lhei=c(.5,6,0),
  #        #sepwidth=c(0.001,0.001),
  #        #sepcolor="black",
  #        #colsep=1:ncol(pcadata_f),
  #        #rowsep=1:nrow(pcadata_f),
  #        keysize = 1) 
  #dev.off()

  #PCA
  pcadata_f <- t(pcadata_f)
  Group <- ifelse(rownames(pcadata_f) %in% cs, "Chromatin State", ###chromatin states
                                            ifelse(rownames(pcadata_f)=="DNase", "DNase I", ###dnase
                                                   ifelse(rownames(pcadata_f) %in% hm, "Histone Modification", ###histone modifications
                                                          "TFBS"))) ###transcription factor binding sites
  pcadata_f <- cbind.data.frame(pcadata_f, Group)

  ##Plots without loadings
  p <- autoplot(prcomp(pcadata_f[,-(dim(pcadata_f)[2])]),
         #loadings = TRUE,
         label = TRUE, 
         label.size = 3,
         label.repel=T,
         data=pcadata_f,
         colour='Group') +
  theme_bw()

  ggsave(p, filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
                             scorepnames[i], sep=""),
         width=8, height=11, units="in", dpi=300)

}
